---
title: "QUANTITATIVE MANAGEMENT MODELING"
author: "Shashidhar Reddy Boreddy"
date: "2022-09-29"
output:
  word_document: default
  pdf_document: default
  html_document: default
pdf_document: default
df_print: paged
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
```{r}
#installation("lpSolve")

library("lpSolve") #Activation of lpSolve Package
```

To solve the problem we need to define the objective, constraints, direction and constants

Objective Function

$$\text{Objective function is to } Max \hspace{.3cm} Z = 420 (Q_1+Q_2+Q_3) + 360 (M_1+M_2+M_3) + 300 (P_1+P_2+P_3)$$

\$\$

\$\$

$$ \text {that can be written as } Z = 420Q_1+360M_1+300P_1+420Q_2+360M_2+300P_2+420Q_3+360M_3+300P_3
$$

Subject to the following constraints

$$
Q_1+M_1+P_1 \le 750 
$$

$$
Q_2+M_2+P_2 \le 900 
$$

$$
Q_3+M_3+P_3 \le 450
$$

$$
20Q_1+15M_1+12P_1 \le 13000
$$

$$
20Q_2+15M_2+12P_2 \le 12000
$$

$$
20Q_3+15M_3+12P_3 \le 5000
$$

$$
Q_1+Q_2+Q_3 \le 900
$$

$$
M_1+M_2+M_3 \le 1200
$$

$$
P_1+P_2+P_3 \le 750 
$$

Non Negativity Constraints

$$
 Q_1,Q_2,Q_3,M_1,M_2,M_3,P_1,P_2,P_3 \ge 0
$$

The above constraints can be written as below

$$
Q_1+M_1+P_1+0Q_2+0M_2+0P_2+0Q_3+0M_3+0P_3 \le 750  
$$

$$
 0Q_1+0M_1+0P_1+Q_2+M_2+P_2+0Q_3+0M_3+0P_3 \le 900
$$

$$
 0Q_1+0M_1+0P_1+0Q_2+0M_2+0P_2+Q_3+M_3+P_3 \le 450
$$

$$
20Q_1+15M_1+12P_1+0Q_2+0M_2+0P_2+0Q_3+0M_3+0P_3 \le 13000
$$

$$
0Q_1+0M_1+0P_1+20Q_2+15M_2+12P_2+0Q_3+0M_3+0P_3 \le 12000
$$

$$
0Q_1+0M_1+0P_1+0Q_2+0M_2+0P_2+20Q_3+15M_3+12P_3 \le 5000
$$

$$
Q_1+0M_1+0P_1+Q_2+0M_2+0P_2+Q_3+0M_3+0P_3 \le 900
$$

$$
0Q_1+M_1+0P_1+0Q_2+M_2+0P_2+0Q_3+M_3+0P_3 \le 1200
$$

$$
0Q_1+0M_1+P_1+0Q_2+0M_2+P_2+0Q_3+0M_3+P_3 \le 750
$$

Describing the Objective Function - f.obj

```{r}
f.obj <- c(420,360,300,420,360,300,420,360,300)
```

Describing the Constraints - f.con

```{r}

f.con <- matrix(c(1,1,1,0,0,0,0,0,0,
                  0,0,0,1,1,1,0,0,0,
                  0,0,0,0,0,0,1,1,1,
                  20,15,12,0,0,0,0,0,0,
                  0,0,0,20,15,12,0,0,0,
                  0,0,0,0,0,0,20,15,12,
                  1,0,0,1,0,0,1,0,0,
                  0,1,0,0,1,0,0,1,0,
                  0,0,1,0,0,1,0,0,1), nrow = 9, byrow=T)

```

Describing the Direction of the constraints - f.dir

```{r}
f.dir <- c('<=',

           '<=',

           '<=',

           '<=',

           '<=',

           '<=',

           '<=',

           '<=',

           '<=')
```

Describing the constants i.e. the right hand side values - f.rhs

```{r}
f.rhs <- c(750,900,450,13000,12000,5000,900,1200,750)
```

Calling the lp function to solve the problem basing the objective function i.e. to maximize the profits

```{r}
lp('max',f.obj,f.con,f.dir,f.rhs)
```

Calling the lp function again to get the values for the variables defined above

```{r}
lp('max',f.obj,f.con,f.dir,f.rhs)$solution
```

