---
title: "Data Envelopment Analysis(DEA)"
author: "Shashidhar Reddy Boreddy"
date: "2022-10-29"
output:
  word_document: default
  html_document:
    df_print: paged
output_values: html_document
---
```{r}
# Uploading The Required Libraries
library(Benchmarking)
library(tidyverse)
```
```{r}
#Compute the Formulation
#In this section, we will create a matrix and values
#creating the vectors with our values
input_values <- matrix(c(150, 400, 320, 520, 350, 320,
0.2, 0.7, 1.2, 2.0, 1.2, 0.7), ncol=2)
output_values <- matrix(c(14000, 14000, 42000, 28000, 19000, 14000,
3500, 21000, 10500, 42000, 25000, 15000), ncol=2)
# Defining column names
colnames(input_values) <- c("Staff Hours Per Day", "Supplies Per Day")
colnames(output_values) <- c("Reimbursed Patient-Days", "Privately Paid Patient-Days")
#To view the input_values values
input_values
# To view the output_values values
output_values
#As we can see, we are obtaining the identical numbers as in the performance data table from the six nursing facilities operated by Hope Valley Health Care Association.
#In the next part, we will conduct a Data Envelopment Analysis (DEA), which is an analytical method that may assist businesses in identifying and allocating resources to improve efficiency and practice.

```
```{r}
#FDH-based DEA Analysis
#Now we'll use FDH to define and compute the DEA analysis.The Free disposability hull (FDH) is the assumption that undesirable inputs and outputs are discarded. "We can always create fewer outputs with more inputs because we have free disposability."
#Giving the input_values and output_values.
Anal.FDH<- dea(input_values,output_values,RTS = "FDH")
#Making a data frame with efficiency values.
EV.FDH <- as.data.frame(Anal.FDH$eff)
#  assigning an appropiate name
colnames(EV.FDH) <- c("Efficiency_FDH")
# Identification of peers
p.FDH <- peers(Anal.FDH)
# assigning an appropiate name for peers
colnames(p.FDH) <- c("Peer1_FDH")
# Using the lambda function, determine the relative weights assigned to peers.
lambda_FDH <- lambda(Anal.FDH)
#  giving Lambda exact column name
colnames(lambda_FDH) <- c("L1_FDH", "L2_FDH", "L3_FDH", "L4_FDH", "L5_FDH", "L6_FDH")
# Creating a tabular data with peer, lambda, and efficiency
peer_lambda_EV.FDH <- cbind(p.FDH, lambda_FDH, EV.FDH)
# displaying  summary chart
peer_lambda_EV.FDH
```
#As we learnt in this session, peers are a good method to discover inefficient DMUs or units, and Lambda is a good approach to find inefficient units.When solving the DEA model, values are the raw weights assigned by peer units.The summary figure above indicates that each DMU or facility is operating at maximum capacity.efficiency. Because each peer was allocated a single unit, the Lambda and efficiency values are both 1as well as

# displaying the Plot  results
```{r}
dea.plot(input_values,output_values,RTS="FDH",ORIENTATION="in-out",txt=TRUE, xlab = "input_values", ylab= "output_values", main="Free disposability hull (FDH) Graph")
```

```{r}
#CRS-based DEA Analysis
#Now we'll formulate and calculate the DEA analysis with Constant Returns to Scale (CRS).The CRS is part of the scaling assumption, and it helps us to evaluate if there are any feasible scaling up or down combinations.
# Giving the input_values and output_values
Anal.CRS <- dea(input_values,output_values,RTS = "CRS")
# observing the effciency values
EV.CRS <- as.data.frame(Anal.CRS$eff)
#  assigning a appropiate name
colnames(EV.CRS) <- c("Efficiency_CRS")
# Identification of peers
Peers_CRS <- peers(Anal.CRS)
# assigning an appropiate name
colnames(Peers_CRS) <- c("Peer1_CRS", "Peer2_CRS", "Peer3_CRS")
# Identifying the relative weights given to the peers using lambda function
lambda_CRS <- lambda(Anal.CRS)
#  assign a appropiate column name for Lambda
colnames(lambda_CRS) <- c("L1_CRS", "L2_CRS", "L3_CRS", "L4_CRS")
# Create a tabular data with peer, lambda, and efficiency
Peers_lambda_EV.CRS <- cbind(Peers_CRS, lambda_CRS, EV.CRS)
#displaying  summary chart
Peers_lambda_EV.CRS
```
#In terms of Constant Returns to Scale (CRS), the facilities 1, 2, 3, and 4 are utilizing all of their efficiency, as demonstrated by the lambdas and peers. Facility 5 and 6, on the other hand, require portions of 1, 2, and 4, as demonstrated by the peers and lambdas above. It suggests that these two facilities (5 and 6) have opportunity to improve because their efficiency rates are 97.74% and 86.74%, respectively.
```{r}
# displaying the Plot  results
dea.plot(input_values,output_values,RTS="crs",ORIENTATION="in-out",
txt=TRUE, xlab = 'input_values', ylab= 'output_values', main="Constant Returns to Scale (CRS) Graph")
```
```{r}
#VRS DEA Analysis
#Now we will construct and calculate the DEA analysis utilizing Variable Returns to Scale (VRS). VRS is also part of the scaling assumption, and it aids in estimating the efficiency of the variables whether An increase or reduction is not proportionate.
# Giving the input_values and output_values
Anal.VRS <- dea(input_values,output_values,RTS = "VRS")
# To observe effciency values
EV.VRS <- as.data.frame(Anal.VRS$eff)
#  assigning an appropiate name
colnames(EV.VRS) <- c("Efficiency_VRS")
# Identify the peers
Peers_VRS <- peers(Anal.VRS)
# assigning an appropiate name
colnames(Peers_VRS) <- c("Peer1_VRS", "Peer2_VRS", "Peer3_VRS")
# Identify the relative weights given to the peers using lambda function
lambda_VRS <- lambda(Anal.VRS)
# To assign an appropiate column name for Lambda
colnames(lambda_VRS) <- c("L1_VRS", "L2_VRS", "L3_VRS", "L4_VRS", "L5_VRS")
# Create a tabular data with peer, lambda, and efficiency
peers_lambda_EV.VRS <- cbind(Peers_VRS, lambda_VRS, EV.VRS)
#displaying  summary chart
peers_lambda_EV.VRS
```
#When we run the Variable Returns to Scale (VRS), we can see that facilities 1, 2, 3, 4, and 5 are all operating at full capacity or efficiency. This is not the case with facility 6, which has an efficiency of 89.63%. Peers and lambdas indicate that facility 6 requires parts of facilities 1, 2, and 5 to be more efficient.
```{r}
# displaying the Plot  results
dea.plot(input_values,output_values,RTS="vrs",ORIENTATION="in-out",
txt=TRUE, xlab ='Imput', ylab = 'output_values', main ="Variable Returns to Scale (VRS) Graph")
```

```{r}
#IRS Analysis for DEA
#Now we'll formulate and compute the DEA analysis with Increasing Returns to Scale (IRS).IRS shows whether or not the operation scale may be created.
# Giving the input_values and output_values
Anal.IRS <- dea(input_values,output_values,RTS = "irs")
# observe effciency values
EV.IRS <- as.data.frame(Anal.IRS$eff)
#  assigning an appropiate name
colnames(EV.IRS) <- c("Efficiency_IRS")
# Identify the peers
Peers_IRS <- peers(Anal.IRS)
#  assign an appropiate name
colnames(Peers_IRS) <- c("Peer1_IRS", "Peer2_IRS", "Peer3_IRS")
# Identify the relative weights given to the peers using lambda function
lambda_IRS <- lambda(Anal.IRS)
#  assigning an appropiate column name for Lambda
colnames(lambda_IRS) <- c("L1_IRS", "L2_IRS", "L3_IRS", "L4_IRS", "L5_IRS")
# Create a tabular data with peer, lambda, and efficiency
peers_lambda_EV.IRS <- cbind(Peers_IRS, lambda_IRS, EV.IRS)
#displaying  summary chart
peers_lambda_EV.IRS
```
#Rising Returns to Scale (IRS) is the same as Variable Returns to Scale (VRS) since facilities 1, 2, 3, 4, and 5 are all operating at full capacity, while facility 6 requires improvements from units 1, 2, and 5 to enhance their efficiency, which is 89.63%.
```{r}
# displaying the Plot  results
dea.plot(input_values,output_values,RTS="irs",ORIENTATION="in-out",
txt=TRUE, xlab = 'input_values', ylab= 'output_values', main="Increasing Returns to Scale (IRS) Graph")
```
```{r}
#DRS for DEA Analysis
#Now we will develop and perform the DEA analysis based on Decreasing Returns to Scale (DRS).DRS is the inverse of IRS in that its purpose is to reduce the operation size on every potential productionprocess.
# Giving the input_values and output_values
Anal.DRS <- dea(input_values,output_values,RTS = "DRS")
# To observe the effciency values
EV.DRS <- as.data.frame(Anal.DRS$eff)
#  assigning an appropiate name
colnames(EV.DRS) <- c("Efficiency_DRS")
# Identifying the peers
Peers_DRS <- peers(Anal.DRS)
#  assigning an appropiate name
colnames(Peers_DRS) <- c("Peer1_DRS", "Peer2_DRS", "Peer3_DRS")
# Identifying the relative weights given to the peers using lambda function
lambda_DRS <- lambda(Anal.DRS)
#  assign an appropiate column name for Lambda
colnames(lambda_DRS) <- c("L1_DRS", "L2_DRS", "L3_DRS", "L4_DRS")
# Create a tabular data with peer, lambda, and efficiency
peers_lambda_EV.DRS <- cbind(Peers_DRS, lambda_DRS, EV.DRS)
#displaying  summary chart
peers_lambda_EV.DRS
```
#Decreasing Returns to Scale (DRS) is effective in facilities 1, 2, 3, and 4. There is need for improvement in facilities 5 and 6. Both require parts of facilities 1, 2, and 4 to attain their maximum efficiency of 1, as shown in the preceding table.
```{r}
# displaying the Plot  results
dea.plot(input_values,output_values,RTS="drs",ORIENTATION="in-out",
txt=TRUE, xlab = 'Imput', ylab= 'output_values', main="Decreasing Returns to Scale (DRS) Graph")
```
```{r}
#FRH DEA Analysis
#Now, we'll use Free Replicability Hull to define and perform the DEA analysis (FRH).Both FRH and FDH employ mixed integer programming, which requires the variables to be integers in order to find the best solution. FRH's purpose is to use random variables to substitute deterministic data.
# Giving the input_values and output_values
Anal.FRH <- dea(input_values,output_values,RTS = "add")
# To observe effciency values
EV.FRH <- as.data.frame(Anal.FRH$eff)
#  assigning an appropiate name
colnames(EV.FRH) <- c("Efficiency_FRH")
# Identifying the peers
Peers_FRH <- peers(Anal.FRH)
#  assign an appropiate name
colnames(Peers_FRH) <- c("peer1_FRH")
# Identifying the relative weights given to the peers using lambda function
lambda_FRH <- lambda(Anal.FRH)
# To assign an appropiate column name for Lambda
colnames(lambda_FRH) <- c("L1_FRH", "L2_FRH", "L3_FRH", "L4_FRH", "L5_FRH", "L6_FRH")
# Create a tabular data with peer, lambda, and efficiency
peers_lambda_EV.FRH <- cbind(Peers_FRH, lambda_FRH, EV.FRH)
#displaying  summary chart
peers_lambda_EV.FRH
```
#All of the DMU in Free Replicability Hull (FRH) are extremely efficient. It behaves similarly to the Free disposability hull (FDH), in that each of its values has its own peer, lambas, and efficiency of 1.
```{r}
# displaying the Plot  results
dea.plot(input_values,output_values,RTS="add",ORIENTATION="in-out",
txt=TRUE, xlab = 'Imput', ylab= 'output_values', main="Free Replicability Hull (FRH) Graph")
```
```{r}
#Comparison of various assumptions
#"All DEA models share the premise of estimating the technology using a minimal extrapolation technique," we taught in this session (DEA Slides). As we can see, FDH is the most compact technology set. It attempts to create fewer outputs (number of patientdays funded by third-party sources and number of patientdays reimbursed privately) with more than 12 inputs (staffing labor and the cost of supplies). Firms normally prefer the FDH model, however it has several downsides owing to its assumptions. As we can see, all of the efficiencies in this model are one, but when compared to other models, it is not as efficient as we believe since we identify areas/units for improvement.VRS is bigger than FDH because it "fills in" the gaps left by FDH.We can observe that unit 6's efficiency can be improved.The charts show that DRS and IRS are greater than VRS. DRS attempts to expand the set for lower input values, whereas the IRS attempts to expand the technology for higher input values. DRS suggests that units 5 and 6 might increase their efficiency, while IRS suggests that facility 6 could as well.CRS is the most extensive technology set, so we can examine whether there is any viable combination to scale up or down. Units 5 and 6 require improvement based on the efficiency numbers.Based on the arrow network we reviewed in class, FRH is larger than FDH but less than CRS.



```


